---
title: '00A - R Configuration'
author: "Emma Bell"
date: '2021-04-05'
output:
  html_document:
    df_print: paged
    toc: yes
    toc_float: true
    toc_depth: 2
    fig_caption: true
---

# Summary {.tabset}

This R Notebook contains code pertaining to the project 2021_03_Bell.

* Aim: To configure my R environment.
* Objectives:
  1. Create objects specifying the path to commonly referenced directories;
  2. Create objects specifying the parameters for generating figures;
  3. Create an object specifying the colour scheme used in figures.

To run these scripts we assume a directory structure as described in the README accompanying this GitHub. I.e.

* code/ - _contains R Notebook(s) and the resulting HTML file(s)_
* data/ - _contains any data used in this project_
  * 01_raw/
  * 02_clean/
  * 03_augmented/
* docs/ - _contains any documents pertaining to this project_
  * Presentation_plan_template.docx
  * Presentation_template.pptx
  * Research_project_plan.docx
* results/ - _contains results files_
  * docs/
  * figures/
  * tables/

## 1. Create objects specifying the path to commonly referenced directories

The parent directory for this project is `2021_03_Bell_cfMeDIP`.

```{r}
code.dir <- file.path("code")
data.dir <- file.path("data")
clean.data.dir <- file.path(data.dir,"02_clean")
augmented.data.dir <- file.path(data.dir,"03_augmented")
docs.dir <- file.path("docs")
results.dir <- file.path("results")
figure.dir <- file.path(results.dir,"figures")
table.dir <- file.path(results.dir,"tables")

dirs <- list(code.dir=code.dir,data.dir=data.dir,clean.data.dir=clean.data.dir,augmented.data.dir=augmented.data.dir,docs.dir=docs.dir,results.dir=results.dir,figure.dir=figure.dir,table.dir=table.dir)
dirs
```

## 2. Create objects specifying the parameters for generating figures

All figures are outputted to the following specifications:

```{r}
units <- "cm"
width <- 6
height <- 6
res <- 480
pointsize <- 6

fig.specs <- list(units = units,
                  width = width,
                  height = height,
                  res = res,
                  pointsize = pointsize)
fig.specs
```

## 3. Create an object specifying the colour scheme used in figures

This R Notebook requires the following packages:

```{r}
library(viridis)
```

The colour scheme used in this R Notebook has not yet been defined:

```{r}
# pal <- inferno(n = 9, begin = 0.2, end = 0.8)
# pal2 <- inferno(n = 9, begin = 0.2, end = 0.8, alpha = 0.5)
# 
# fig.cols <- list(
#     Donor = c(`Donor 1`=pal2[1], `Donor 2`=pal[1], `Donor 3`=pal[2]),
#     Stimulated = c(Unstimulated="#DEA3AF",Stimulated=pal[5]),
#     DAC = c(Untreated="lightgrey",Treated=pal[7]))
# fig.cols
# 
# simple.cols <- unlist(fig.cols)[c(4,5,7)]
# simple.cols
```


```{r}
r.config <- list(dirs = dirs,
                 fig.specs = fig.specs)
                 # fig.cols = fig.cols,
                 # simple.cols = simple.cols)
r.config
```

```{r}
saveRDS(object = r.config, file = file.path(dirs$code.dir,"r_config.RDS"))
```

